### 2020-07-13 ISSTA/introduction.tex
shrinking agian

A system is deterministic if, given the system's complete state at a point in
time, it is possible, in principle, to predict its future behavior
perfectly.  In the real world,
prediction may be possible but  impractical.  We write
complex software systems because we cannot predict their
behavior.  As a consequence, rather than
defining determinism in terms of prediction, we usually 
say that a system is deterministic if, \emph{given a certain limited abstraction of state
and inputs, observable behavior is repeatable}.  %This abstraction,
%for most software, is not expected to include many elements outside of
%the software system itself.

Because the
programmer's abstraction of the system ignores a large number of
details, very few tests are ``deterministic'' in the sense
that they eliminate all changes between executions.  Running the same test
twice almost always results in differences, given a low enough level of
abstraction, since the system load,
cache contents, branch predictor history, etc. are almost never
controlled for; however, what matters is when
some kind of nondeterminism unexpectedly impacts computed values at a
higher level of abstraction.

@@

Complex
modern software systems usually include a large set of
\emph{regression tests}.  A regression test suite is a
set of tests that can be run against softwarre every time it
is modified, to ensure that the modification has not broken the system.  \emph{Flaky tests} \cite{miccoflaky} are regression
tests that fail in an intermittent, unreliable fashion.  The essence of a flaky
test is that, for the same snapshot of test code and code under test
(CUT), it sometimes fails and sometimes passes: the pass/fail result (disposition) of the
test is not a deterministic property of the test code, code under
test, and testing environment.  This produces three serious
problems: first, a flaky test often wastes developer time and delays
software changes by forcing the investigation of code-under-test that
is not actually incorrect.  Second, failures in flaky tests are often ignored, and therefore serious software faults may
be missed.  Finally, to mitigate these problems, flaky tests are often
run multiple times, wasting computing resources and
delaying acceptance of code changes.  As an analogy, we note that  a canary in a coal mine is of
little use if canaries frequently become ill for reasons unrelated to
the presence of toxic gases.  Mining may stop for no good reason, or
miners may learn to ignore the canary, leading to tragedy; a third,
more ``practical'' option is that miners may carry so many redundant
canaries into the coal mine that canary-care itself becomes a serious burden.

Flaky tests are, for us, simply a special case of general test
nondeterminism, where the nondeterminism of test values is sufficient
to cause the pass/fail result of the test to vary.  The definitions
and techniques proposed in this paper all apply to flaky tests, as a
special case of various kinds of \emph{horizontal} nondeterminism
described below.  Our focus is on detecting sources of
flaky-ness in libraries, \emph{before} they propagate.
%unlike all other tools and
%approaches we are aware of, is on detecting the \emph{sources} of
%flaky-ness \emph{before} they propagate to cause actual test failure.

@@

{\bf Contributions:} This paper proposes (1) a number of formal definitions of types of
nondeterminism (\emph{horizontal} and \emph{vertical}) and (2) an implementation, based on these definitions, for detecting and debugging
nondeterminism in property-based testing.  The implementation is based
on an approach where (3) horizontal determinism is considered as a
kind of \emph{reflexive differential testing} (4) vertical
determinism is specialized to the common case of \emph{failure
  determinism}, and (5)  in both cases the formalism is made practical
by using the \emph{value pool} model of unit tests.
We also introduce necessary modifications to the widely used delta-debugging algorithm in order to better handle
nondeterminism as a test property.

@@

Our methods enable automated production of
nondeterminism-free regression tests even for libraries with some
sources of nondeterminism, documentation of sources of
nondeterminism that might produce problems for manually-constructed
tests, and, most importantly, detection and debugging of 
unexpected nondeterminism bugs.  We use a set
of case studies. including real-world, widely-used, Python libraries, to demonstrate the
utility of our ideas.  Our novel notion of failure determinism directly
produces a more than 5\% improvement in mutation score for an already highly
effective automated test generation tool for a file system, with no
additional specification or test design burden.

>>>>

A system is deterministic if, given the system's complete state at a point in
time, it is possible, in principle, to predict its future behavior
perfectly.  In the real world,
prediction may be possible but  impractical, or some details neither
predictable nor interesting.  We write
complex software systems because we cannot predict their
behavior, and we usually want to abstract away from machine-level details.  As a consequence, rather than
defining determinism in terms of prediction, we usually 
say that a system is deterministic if, \emph{given a certain limited
  higher-level abstraction of state
and inputs, observable behavior is repeatable}.  %This abstraction,
%for most software, is not expected to include many elements outside of
%the software system itself.

\begin{comment}
Because the
programmer's abstraction of the system ignores a large number of
details, very few tests are ``deterministic'' in the sense
that they eliminate all changes between executions.  Running the same test
twice almost always results in differences, given a low enough level of
abstraction, since the system load,
cache contents, branch predictor history, etc. are almost never
controlled for; however, what matters is when
some kind of nondeterminism unexpectedly impacts computed values at a
higher level of abstraction.
\end{comment}

@@

Complex
modern software systems usually include a large set of
\emph{regression tests}.  A regression test suite is a
set of tests that can be run against softwarre every time it
is modified, to ensure that the modification has not broken the system.  \emph{Flaky tests} \cite{miccoflaky} are regression
tests that fail in an intermittent, unreliable fashion.  The essence of a flaky
test is that, for the same snapshot of test code and code under test
(CUT), it sometimes fails and sometimes passes: the pass/fail result (disposition) of the
test is not a deterministic property of the test code, code under
test, and testing environment.  This produces three serious
problems: first, a flaky test often wastes developer time and delays
software changes by forcing the investigation of code-under-test that
is not actually incorrect.  Second, failures in flaky tests are often ignored, and therefore serious software faults may
be missed.  Finally, to mitigate these problems, flaky tests are often
run multiple times, wasting computing resources and
delaying code changes.  Flaky tests are, for us, simply a special case of general test 
nondeterminism, in particular the 
\emph{horizontal} nondeterminism 
described below.  Our focus is on detecting sources of 
flaky-ness, \emph{before} they propagate.
\begin{comment}
  As an analogy, we note that  a canary in a coal mine is of
little use if canaries frequently become ill for reasons unrelated to
the presence of toxic gases.  Mining may stop for no good reason, or
miners may learn to ignore the canary, leading to tragedy; a third,
more ``practical'' option is that miners may carry so many redundant
canaries into the coal mine that canary-care itself becomes a serious burden.
\end{comment}

%unlike all other tools and
%approaches we are aware of, is on detecting the \emph{sources} of
%flaky-ness \emph{before} they propagate to cause actual test failure.

@@

{\bf Contributions:} This paper proposes (1) a number of formal definitions of types of
nondeterminism (\emph{horizontal} and \emph{vertical}) and (2) an implementation, based on these definitions, for detecting and debugging
nondeterminism in property-based testing.  The implementation is based
on an approach where (3) horizontal determinism is considered as a
kind of \emph{reflexive differential testing} (4) vertical
determinism is specialized to the common case of \emph{failure
  determinism}, and (5)  in both cases the formalism is made practical
by using the \emph{value pool} model of unit tests.
We also introduce necessary modifications to the widely used delta-debugging algorithm in order to better handle
nondeterminism as a test property.  Evaluating these approaches with
realistic Python libraries, we show large improvements to both fault
detection and test reduction.

@@

\begin{comment}
Our methods enable automated production of
nondeterminism-free regression tests even for libraries with some
sources of nondeterminism, documentation of sources of
nondeterminism that might produce problems for manually-constructed
tests, and, most importantly, detection and debugging of 
unexpected nondeterminism bugs.  We use a set
of case studies. including real-world, widely-used, Python libraries, to demonstrate the
utility of our ideas.  Our novel notion of failure determinism directly
produces a more than 5\% improvement in mutation score for an already highly
effective automated test generation tool for a file system, with no
additional specification or test design burden.
\end{comment}
